\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{KARTHIK THYAGARAJAN}}
\end{center}

\vspace{-7mm}

\begin{center}
    \small{
    \href{karthik6002@gmail.com}{karthik6002@gmail.com} | 
    \href{kthyagar@purdue.edu}{kthyagar@purdue.edu}
    
    \href{https://www.karthikthyagarajan.com}
    {karthikthyagarajan.com} | 
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/karthikthyagarajan06}{linkedin.com/in/karthikthyagarajan06/} | 
    \socialicon{\faGithub} \href{https://github.com/karthikcsq}{github.com/karthikcsq} 
    }
\end{center}

\section{\textbf{Education}}
\resumeSubHeadingListStart


  \resumeSubheading
  { Purdue University }
  { West Lafayette, Indiana }
  { B.S. of Computer Science \& Artificial Intelligence - 4.0 GPA }
  { August 2024 - May 2027 (Expected) }


\resumeSubHeadingListEnd

\vspace{-6mm}

\section{\textbf{Skills}}
\resumeHeadingSkillStart

  \resumeSubItem{AI/ML: }{LLM (LangChain, RAG, CoT/Reasoning, RLHF), Agents, MCP, PyTorch, Tensorflow, GAN, RL, Diffusion, Graph Neural Networks}

  \resumeSubItem{Data Science: }{Numpy, Pandas, PostgreSQL, NoSQL}

  \resumeSubItem{Languages \& Frameworks: }{Python, Java, C++, C, JS/TS, HTML/CSS, React, Flask, Gradle}

  \resumeSubItem{Quantum Computing: }{Qiskit, VQE, QAOA, Quantum ML}

  \resumeSubItem{Other: }{REST API, AWS System Design, GCP, OAuth, Git, Docker, Linux}

\resumeHeadingSkillEnd

\section{\textbf{Experience}}
\resumeSubHeadingListStart

  \resumeSubheading
  {Machine Learning Researcher}
  {Silver Spring, MD}
  {Peraton Labs (Internship \& Part-Time Co-op)}
  {Jun 2025 - Present }
  \resumeItemListStart
  
    \item Developed a novel reinforcement learning (RL) agent for IoT malware detection, reducing exploration latency by 35\% and increasing detection coverage by 25\% compared to brute-force baselines.
  
    \item Built a heterogeneous graph neural network with autoencoders to model inter-device relationships and accelerate RL policy convergence, improving anomaly detection accuracy.
  
  \resumeItemListEnd

  \resumeSubheading
  {Computer Vision Researcher}
  {Remote}
  {Memories.ai (Part-Time)}
  {Feb 2025 - Aug 2025 }
  \resumeItemListStart
  
    \item Engineered and deployed a scalable video memory framework for AR applications, enabling persistent spatial and contextual awareness while optimizing throughput for speed and scalability.
  
    \item {'Designed and published a Python SDK for the Mavi platform (PyPI': 'https://pypi.org/project/pymavi/), streamlining developer workflows for video analysis.'}
  
  \resumeItemListEnd

  \resumeSubheading
  {Undergraduate Robotics Researcher}
  {West Lafayette, IN}
  {IDEAS Lab, Purdue University (Part-Time)}
  {Mar 2025 - Jun 2025 }
  \resumeItemListStart
  
    \item Built real-time SLAM and novel view-synthesis pipelines in Python and C++, improving 3D scene reconstruction accuracy by 25\% while ensuring deployment safety and reliability.
  
    \item Optimized autonomous navigation algorithms, reducing mapping latency through performance tuning.
  
  \resumeItemListEnd

  \resumeSubheading
  {Undergraduate Data Science Researcher}
  {West Lafayette, IN}
  {The Data Mine Corporate Partners, Purdue University (Part-Time)}
  {Aug 2024 - Dec 2024 }
  \resumeItemListStart
  
    \item Designed an end-to-end weed detection pipeline with Python, TensorFlow, and PostgreSQL; optimized queries for 40\% faster data retrieval.
  
    \item Built semantic segmentation and localization models for drone-based weed detection, reducing herbicide usage by 60\% and improving efficiency 50\% over ground-vehicle methods.
  
  \resumeItemListEnd

  \resumeSubheading
  {ML Science \& Engineering Apprenticeship}
  {Washington, D.C.}
  {Naval Research Laboratory (Full-Time)}
  {Jun 2023 - Aug 2023 }
  \resumeItemListStart
  
    \item Led a 4-member team applying UNets, Transformers, and GANs to underwater acoustics, improving transmission loss prediction accuracy by 20\% compared to physics-based models.
  
    \item Prototyped and deployed a secure Retrieval-Augmented Generation (RAG) system, ensuring data confidentiality and operational reliability.
  
  \resumeItemListEnd

\resumeSubHeadingListEnd

\section{\textbf{Projects}}
\resumeSubHeadingListStart

\resumeProject
  {In The Loop}
  {Tools: Next.js, React, TypeScript, Tailwind CSS, Vercel}
  {Ongoing}
  {\href{https://in-the-loop-ai.vercel.app/}{https://in-the-loop-ai.vercel.app/} }
\resumeItemListStart
  
  \item Developed a platform to streamline AI interactions by reducing token wastage and clarifying user intent, improving efficiency of LLM-driven workflows.
  
  \item Implemented streaming with a deployed LangGraph agent backend to handle within-thread communications and user interrupts.
  
\resumeItemListEnd

\resumeProject
  {Storytime.ai}
  {Tools: Next.js, React, TypeScript, Tailwind CSS, Vercel}
  {Ongoing}
  {\href{https://storytime-sepia.vercel.app/}{https://storytime-sepia.vercel.app/} }
\resumeItemListStart
  
  \item Built an AI-driven news aggregation platform that clusters stories and updates, reducing information overload and improving content personalization.
  
  \item Integrated GPT-4o for dynamic summarization, making use of vector databases for efficient similarity search.
  
\resumeItemListEnd

\resumeProject
  {Personal Website}
  {Tools: Next.js, React, TypeScript, Tailwind CSS, Vercel, Pinecone, AWS S3, Python}
  {Ongoing}
  {\href{https://github.com/karthikcsq/personalsite}{https://github.com/karthikcsq/personalsite} }
\resumeItemListStart
  
  \item Developed and deployed a personal portfolio site with Vercel and AWS S3, showcasing projects, blogs, and image galleries; optimized for CDN-based global delivery.
  
  \item Integrated a Pinecone-powered RAG pipeline to enable semantic search across Markdown-based project documentation.
  
\resumeItemListEnd

\resumeProject
  {Verbatim}
  {Tools: OpenAI APIs, Google Cloud APIs, Next.js, Vercel}
  {Feb 2025}
  {\href{https://github.com/karthikcsq/verbatim}{https://github.com/karthikcsq/verbatim} }
\resumeItemListStart
  
  \item Created a multi-function video platform for summarization, translation, voice cloning, and lip-sync, deployed at https://www.getverbatim.tech.
  
  \item Automated workflows with Whisper (ASR), GPT-4o (summarization), Google Translate (translation), Eleven Labs (voice cloning), and Twelve Labs (video Q\&A).
  
\resumeItemListEnd

\resumeProject
  {Photonic Implementation of Quantum Key Distribution}
  {Tools: Oscilloscope, Python, NumPy}
  {Oct 2023 – May 2024}
  {\href{https://arxiv.org/abs/2509.04389}{https://arxiv.org/abs/2509.04389} }
\resumeItemListStart
  
  \item Built and aligned a photonic QKD prototype using lasers, polarizers, phase modulators, and beamsplitters to implement polarization-based key exchange.
  
  \item Automated data parsing and thresholding (0.004 mW cutoff) for bit-sequence extraction, basis sifting, and noise analysis with Python.
  
\resumeItemListEnd

\resumeProject
  {Quantum Racer (Educational Android Game)}
  {Tools: Java, Android SDK, Gradle, XML Layouts}
  {Aug 2022 – Dec 2022}
  {\href{https://github.com/karthikcsq/QuantumCarGame\_Self}{https://github.com/karthikcsq/QuantumCarGame\_Self} }
\resumeItemListStart
  
  \item Designed and implemented an educational Android game translating quantum mechanics concepts (superposition, measurement, decoherence) into racing gameplay.
  
  \item Delivered complete game physics, touch-input UI, and asset pipeline, packaging the final APK for distribution and educational outreach.
  
\resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}